Equations & R Code

### 2016-12-28 manuscript/coexistence-stability_ms.Rmd
updates small grammatical issues

RESULTS
-------
When we allowed the variance of the environment to determine which of four initial species coexisted, similar to a community assembly experiment, we found a positive relationship between richness and variability (Fig. 2A,C).
This was true for the storage effect, where coexistence is maintained by fluctuating live-to-dormant transition rates ($\gamma$), and for relative nonlinearity, where coexistence is maintained by annual resource pulses.
The relationship is driven by the fact that increasing environmental variability increases the strength of both coexistence mechanisms (Fig. S1-2).
More variable conditions promoted species richness, creating a positive relationship between diversity and variability.

@@

FIGURES
-------
```{r model_types, cache=FALSE, warning=FALSE, message=FALSE, eval=TRUE, dev="png", fig.height=3, fig.width=5, dpi=300,fig.cap="Resource uptake functions and example time series of (un)correlated germination fractions for the storage effect (A,B) and relative nonlinearity (C,D) formulations of the consumer-resource model. The resource uptake functions for both species are equivalent for the storage effect, but their live-to-dormant transition fractions ($gamma$) are uncorrelated in time. The opposite is true for relative nonlinearity: the two species have unique resource uptake functions, but their live-to-dormant transition fractions ($gamma$) are perfectly correlated in time."}
library(ggplot2)
library(ggthemes)
library(mvtnorm)
library(gridExtra)
library(viridis)
library(RColorBrewer)

>>>>

RESULTS
-------
When we allowed the variance of the environment to determine which of four initial species coexisted, similar to a community assembly experiment, we found a positive relationship between richness and variability (Fig. 2A,C).
This was true for the storage effect, where coexistence is maintained by fluctuating dormant-to-live transition rates ($\gamma$), and for relative nonlinearity, where coexistence is maintained by annual resource pulses.
The relationship is driven by the fact that increasing environmental variability increases the strength of both coexistence mechanisms (Fig. S1-2).
More variable conditions promoted species richness, creating a positive relationship between diversity and variability.

@@

FIGURES
-------
```{r model_types, cache=FALSE, warning=FALSE, message=FALSE, eval=TRUE, dev="png", fig.height=3, fig.width=5, dpi=300,fig.cap="Resource uptake functions and example time series of (un)correlated germination fractions for the storage effect (A,B) and relative nonlinearity (C,D) formulations of the consumer-resource model. The resource uptake functions for both species are equivalent for the storage effect, but their dormant-to-live transition fractions ($\\gamma$) are uncorrelated in time. The opposite is true for relative nonlinearity: the two species have unique resource uptake functions, but their dormant-to-live transition fractions ($\\gamma$) are perfectly correlated in time."}
library(ggplot2)
library(ggthemes)
library(mvtnorm)
library(gridExtra)
library(viridis)
library(RColorBrewer)

### 2016-12-28 manuscript/coexistence-stability_ms.tex
updates small grammatical issues

When we allowed the variance of the environment to determine which of
four initial species coexisted, similar to a community assembly
experiment, we found a positive relationship between richness and
variability (Fig. 2A,C). This was true for the storage effect, where
coexistence is maintained by fluctuating live-to-dormant transition
rates (\(\gamma\)), and for relative nonlinearity, where coexistence is
maintained by annual resource pulses. The relationship is driven by the
fact that increasing environmental variability increases the strength of
both coexistence mechanisms (Fig. S1-2). More variable conditions
promoted species richness, creating a positive relationship between
diversity and variability.

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-model_types-1.png}
\caption{Resource uptake functions and example time series of
(un)correlated germination fractions for the storage effect (A,B) and
relative nonlinearity (C,D) formulations of the consumer-resource model.
The resource uptake functions for both species are equivalent for the
storage effect, but their live-to-dormant transition fractions
(\(gamma\)) are uncorrelated in time. The opposite is true for relative
nonlinearity: the two species have unique resource uptake functions, but
their live-to-dormant transition fractions (\(gamma\)) are perfectly
correlated in time.}
\end{figure}

>>>>

When we allowed the variance of the environment to determine which of
four initial species coexisted, similar to a community assembly
experiment, we found a positive relationship between richness and
variability (Fig. 2A,C). This was true for the storage effect, where
coexistence is maintained by fluctuating dormant-to-live transition
rates (\(\gamma\)), and for relative nonlinearity, where coexistence is
maintained by annual resource pulses. The relationship is driven by the
fact that increasing environmental variability increases the strength of
both coexistence mechanisms (Fig. S1-2). More variable conditions
promoted species richness, creating a positive relationship between
diversity and variability.

@@

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-model_types-1.png}
\caption{Resource uptake functions and example time series of
(un)correlated germination fractions for the storage effect (A,B) and
relative nonlinearity (C,D) formulations of the consumer-resource model.
The resource uptake functions for both species are equivalent for the
storage effect, but their dormant-to-live transition fractions
(\(\gamma\)) are uncorrelated in time. The opposite is true for relative
nonlinearity: the two species have unique resource uptake functions, but
their dormant-to-live transition fractions (\(\gamma\)) are perfectly
correlated in time.}
\end{figure}
